Analytical Model for the Current Density in the Electrochemical Synthesis of Porous Silicon Structures with a Lateral Gradient

### 2021-01-09 paper.tex
Remove highlighted text

\documentclass[review,sort&compress]{cas-sc}
%\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[numbers]{natbib}
%\usepackage[noblocks]{authblk}
%\usepackage{authblk}
%\usepackage[•]{•}ckage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\usepackage{showkeys}
%\usepackage{ieeetr}
\usepackage{bm}
\usepackage{hyperref}
%\usepackage[normalem]{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newif{\ifinclude}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
\newcommand{\notaV}[1]{{\color{red}+V:#1+}}

@@

In Fig. \ref{fig:SI3} we show a photograph of one of our samples,
$S_3$
prepared as described in Sec. \ref{sec:fabrication-ps-grin}, with the
same conditions as those corresponding to Fig.~\ref{fig:DR1} applying
a current
$I_3=20\,\text{mA}$ during a time $t=250\,s$. We notice a series of
visible interference fringes that get wider as we move towards the
right end of the sample, consistent with a inhomogeneous film that
gets thinner towards the right, and qualitatively consistent with
Fig. \ref{fig:DR1} that shows a current density that decays towards
the right. Equal color lines seem to correspond to iso-current lines of
Fig. \ref{fig:SI3}, except very close to the the walls of the cell,
where the film rapidly becomes very narrow. The reason is that there
is a small region below the cell walls where the electrolyte penetrates
up to the sealing o-ring (see upper panel of
Fig. \ref{fig:DE1}) and towards which the current leaks from the
neighborhood of the wall. The width of this region is
$w=0.14\,\text{cm}$. Thus, we may expect our formula \eqref{Eq:J}
to {\em fail} within that region and close to the border, at distances of the order of the radius
of the cross-section of the o-ring, about a millimeter. The
figure shows eight positions
$x'_n=0.2\,\text{cm},0.4\,\text{cm},\ldots,1.6\,\text{cm}$ on which we
measured the near normal incidence reflection spectra of the
sample. Here, we defined $x'_n=x_n+w$ as the distance to the edge of
the etched sample, which corresponds to the position of the sealing o-ring,
whereas $x_n$ is the corresponding distance to the wall of the
cell.

From Eq. \eqref{Eq:J} we evaluate the
normalized current density $j_\perp/I$ expected at the positions $n$ indicated in
Fig. \ref{fig:SI3}. We included an estimated uncertainty in the
distance to the wall of the cell, and the corresponding (asymmetrical)
uncertainty in the computed current density. This
uncertainty arises from the uncontrolled deformation of the o-ring as
it is pressed against the wafer to seal in the electrolyte, so that
its distance to the wall of the cell is ill defined, and we estimate
it as the radius of the o-ring. \notaL{Would it be a good idea to use a
  larger uncertainty? 1mm? The beam spot is 2mm wide.}
(Table \ref{t:xj}).
\begin{table}
  \centering
  \renewcommand{\arraystretch}{1.1}
   \begin{tabular}{rrr}
     \(x'_n\)(cm) & \(x\)(cm)& \(j_\perp/I\) (\(\text{cm}^{-2})\)\\
     from edge& from wall&\\
     \hline
     0.2 &$ 0.06\pm0.05$ & $0.722^{+0.003}_{-0.007}$\\
     0.4 &$ 0.26\pm0.05$ & $0.672^{+0.018}_{-0.021}$\\
     0.6 &$ 0.46\pm0.05$ & $0.577^{+0.027}_{-0.028}$\\
     0.8 &$ 0.66\pm0.05$ & $0.464^{+0.028}_{-0.028}$\\
     1.0 &$ 0.86\pm0.05$ & $0.360^{+0.025}_{-0.023}$\\
     1.2 &$ 1.06\pm0.05$ & $0.275^{+0.019}_{-0.018}$\\
     1.4 &$ 1.26\pm0.05$ & $0.211^{+0.014}_{-0.013}$\\
     1.6 &$ 1.46\pm0.05$ & $0.167^{+0.010}_{-0.009}$\\
  \end{tabular}
  \caption{Normalized current density $j_\perp/I$ expected at different positions $x'_n$.}
  \label{t:xj}
\end{table}

In Fig. \ref{fig:sem} we show some SEM images of the sample $S_3$,
including top views and lateral views taken after
the optical characterization was completed and the sample was cut
along its center-line (see Sec. \ref{sec:R}) from
three regions around the left side, the center, and the right side
of the sample shown in Fig. \ref{fig:SI3}.
\begin{figure}
  \centering
  \includegraphics[width=.3\textwidth]{sema}
  \includegraphics[width=.3\textwidth]{semb}
  \includegraphics[width=.3\textwidth]{semc}
  \includegraphics[width=.3\textwidth]{semd}
  \includegraphics[width=.3\textwidth]{seme}
  \includegraphics[width=.3\textwidth]{semf}
  \caption{Top ((a), (b), and (c)) and lateral ((d), (e), and (f)) SEM
    micrographs of the sample $S_3$ taken from a region corresponding to the left
    side ((a) and (d)), center ((b) and (e)), and right side ((c) and
    (f)) along the center-line shown in Fig. \ref{fig:SI3}.}
  \label{fig:sem}
\end{figure}
We confirm that as we move away from the electrode, the pore
size and pore density diminish (panels (a) to (c) of
Fig. \ref{fig:sem}) and the sample becomes much thinner (panels (d) to
(f)). We remark that these micrographs were taken at three positions
that do not correspond to the eight locations at which we measured the
optical spectra. Thus, we didn't use them to obtain quantitatively the
thickness nor the porosity of the PS layer, but to verify
qualitative our expected results (Fig. \ref{fig:DE1}) and our
actual results (Table \ref{t:jpdv}) obtained from our calculation and
the optical spectra, as explained below.

@@

The results obtained from the reflectance fits are summarized in table
\ref{t:jpdv}.
\begin{table}
\centering
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{lrrrrr}
  Sample & position & density & porosity &
  thickness & rate\\
  ($I$ (mA)) &$x'_n$ (cm)&  $j$ ($\text{mA}/\text{cm}^2$) & $p$
       & $d$ ($\mu\text{m}$) & $v$ (nm/s)\\
\hline
$S_1$(5) &0.2 &$ 3.61^{+0.014}_{-0.03}  $&$0.562\pm0.031$ &$0.381\pm0.021$ &$   1.524\pm0.084$ \\
         &0.4 &$ 3.36^{+0.09}_{-0.11}   $&$0.588\pm0.019$ &$0.403\pm0.014$ &$  1.611\pm0.057$  \\
         &$0.6$  &$ 2.88^{+0.13}_{-0.14}$&$0.582\pm0.024$ &$0.342\pm0.015$ &$   1.366\pm0.060$ \\
         &$0.8$ &$ 2.32^{+0.14}_{-0.14} $&$0.566\pm0.022$ &$0.278\pm0.011$ &$  1.113\pm0.044$ \\
         &$1.0$ &$ 1.80^{+0.13}_{-0.12} $&$0.561\pm0.021$ &$0.224\pm0.009$ &$  0.897\pm0.034$ \\
         &$1.2$ &$ 1.37^{+0.10}_{-0.09} $&$0.561\pm0.019$ &$0.190\pm0.007$ &$  0.761\pm0.027$ \\
         &$1.4$ &$ 1.06^{+0.07}_{-0.06} $&$0.556\pm0.018$ &$0.153\pm0.005$ &$  0.611\pm0.021$ \\
         &$1.6$ &$ 0.83^{+0.05}_{-0.04} $&$0.556\pm0.016$ &$0.124\pm0.004$ &$  0.497\pm0.016$ \\
$S_2$(10) &$0.2$ &$ 7.22^{+0.03}_{-0.07} $&$0.635\pm0.040$ &$0.686\pm0.054$ &$  2.744\pm0.216$ \\
         &$0.4$ &$ 6.72^{+0.02}_{-0,21} $&$0.644\pm0.018$ &$0.694\pm0.025$ &$  2.777\pm0.101$ \\
         &$0.6$ &$ 5.77^{+0.27}_{-0.28} $&$0.640\pm0.033$ &$0.592\pm0.037$ &$  2.368\pm0.149$ \\
         &$0.8$ &$ 4.64^{+0.28}_{-0.28} $&$0.624\pm0.034$ &$0.530\pm0.034$ &$  2.118\pm0.138$ \\
         &$1.0$ &$ 3.60^{+0.25}_{-0.23} $&$0.612\pm0.030$ &$0.470\pm0.027$ &$  1.879\pm0.107$ \\
         &$1.2$ &$ 2.75^{+0.19}_{-0.18} $&$0.603\pm0.034$ &$0.414\pm0.026$ &$  1.658\pm0.104$ \\
         &$1.4$ &$ 2.11^{+0.14}_{-0.13} $&$0.594\pm0.028$ &$0.350\pm0.018$ &$  1.401\pm0.073$ \\
         &$1.6$ &$ 1.67^{+0.10}_{-0.09} $&$0.583\pm0.024$ &$0.302\pm0.014$ &$  1.207\pm0.054$ \\
$S_3$(20) &$0.2$ &$14.45^{+0.06}_{-0.14} $&$0.688\pm0.019$ &$1.208\pm0.047$ &$  4.834\pm0.188$ \\
         &$0.4$ &$ 13.44^{+0.35}_{-0.41}$&$0.718\pm0.024$ &$1.205\pm0.057$ &$  4.820\pm0.228$ \\
         &$0.6$ &$ 11.54^{+0.53}_{-0.55}$&$0.706\pm0.027$ &$1.050\pm0.058$ &$  4.199\pm0.232$ \\
         &$0.8$ &$  9.29^{+0.57}_{-0.55}$&$0.636\pm0.063$ &$0.766\pm0.088$ &$  3.063\pm0.354$ \\
         &$1.0$ &$  7.20^{+0.49}_{-0.47}$&$0.626\pm0.035$ &$0.540\pm0.037$ &$  2.158\pm0.147$  \\
         &$1.2$ &$  5.50^{+0.38}_{-0.36}$&$0.606\pm0.043$ &$0.449\pm0.035$ &$  1.797\pm0.140$ \\
         &$1.4$ &$  4.22^{+0.28}_{-0.26}$&$0.593\pm0.026$ &$0.369\pm0.018$ &$  1.478\pm0.071$ \\
         &$1.6$ &$  3.33^{+0.19}_{-0.17}$&$0.590\pm0.022$ &$0.338\pm0.014$ &$  1.352\pm0.057$ \\
\end{tabular}
\caption{\label{t:jpdv}
  Current density and fitted parameters for several positions on
  three samples:  porosity, thickness, and etching rate.}
\end{table}
The uncertainties in the fitted parameters $p$, $d$, and $v$ were
chosen as those that increase the sum of squared errors by 10\% with
respect to its minimum value.

From the data in Table \ref{t:jpdv} we can plot the fitted porosity vs.
the calculated density current $j_\perp$, as shown for our three
samples in Fig. \ref{fig:p}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pvsjerr}
  \caption{Porosity vs. current density for the three samples
    $S_1$, $S_2$, $S_3$. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$ (see text). We include a linear fit of the form
    $p=mj_\perp+b$ with parameters
    $m=(0.0122\pm0.001)\frac{\text{cm}^2}{\text{mA}}$ and
    $b=0.551\pm.005$.
    }
  \label{fig:p}
\end{figure}
Notice that for each sample the data points lie around straight lines,
except for one outlier point in each corresponding to position
$x'_1$. As discussed in Sec. \ref{sec:ps-grin-single}, those points
were very close to a wall of the electrolytic cell, so they were
affected by leakage currents towards the underside of the wall.
For this reason, we exclude those points from the following
analysis. We made a linear fit of the form $p=mj_\perp+b$ obtaining
\begin{equation}\label{eq:p}
  p\approx (0.0122\pm0.001)\frac{\text{cm}^2}{\text{mA}} j_\perp+(0.551\pm.005).
\end{equation}
Thought the fit is reasonably good, it is noticeable that most of the data from
sample $S_2$ lie to the left of the fitted line while most of the data
from the other samples lie to the right. This discrepancies may be due
to the uncertainty in the positions $x_n$ (see Table \ref{t:xj}) due
to the ill defined distance from the edge of the sample (which roughly
corresponds to the position of the o-ring) to the edge of the cell. A
deformation of the o-ring when the cell is pressed against the wafer
would be equivalent to a rigid shift of the sample, i.e., to adding a
constant to all the positions $x_n$. Thus it is likely that the sign
and magnitude of that uncontrolled constant displacement changes among
samples.

>>>>

\documentclass[review,sort&compress]{cas-sc}
%\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[numbers]{natbib}
%\usepackage[noblocks]{authblk}
%\usepackage{authblk}
%\usepackage[•]{•}ckage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
%\usepackage{showkeys}
%\usepackage{ieeetr}
\usepackage{bm}
\usepackage{hyperref}
%\usepackage[normalem]{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
% \newif{\ifinclude}
%\usepackage{soul}
%\sethlcolor{yellow}
%\newcommand{\hl}[1]{{\color{orange}#1}}
%\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
%\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
%\newcommand{\notaV}[1]{{\color{red}+V:#1+}}

@@

In Fig. \ref{fig:SI3} we show a photograph of one of our samples,
$S_3$,
prepared as described in Sec. \ref{sec:fabrication-ps-grin}, with the
same conditions as those corresponding to Fig.~\ref{fig:DR1} applying
a current
$I_3=20\,\text{mA}$ during a time $t=250\,s$. We notice a series of
visible interference fringes that get wider as we move towards the
right end of the sample, consistent with a inhomogeneous film that
gets thinner towards the right, and qualitatively consistent with
Fig. \ref{fig:DR1} that shows a current density that decays towards
the right. Equal color lines seem to correspond to iso-current lines of
Fig. \ref{fig:SI3}, except very close to the the walls of the cell,
where the film rapidly becomes very narrow. The reason is that there
is a small region below the cell walls where the electrolyte penetrates
up to the sealing o-ring (see upper panel of
Fig. \ref{fig:DE1}) and towards which the current leaks from the
neighborhood of the wall. The width of this region is
$w=0.14\,\text{cm}$. Thus, we may expect our formula \eqref{Eq:J}
to {\em fail} within that region and close to the border, at distances of the order of the radius
of the cross-section of the o-ring, about a millimeter. The
figure shows eight positions
$x'_n=0.2\,\text{cm},0.4\,\text{cm},\ldots,1.6\,\text{cm}$ on which we
measured the near normal incidence reflection spectra of the
sample. Here, we defined $x'_n=x_n+w$ as the distance to the edge of
the etched sample, which corresponds to the position of the sealing o-ring,
whereas $x_n$ is the corresponding distance to the wall of the
cell.

From Eq. \eqref{Eq:J} we evaluate the
normalized current density $j_\perp/I$ expected at the positions $n$ indicated in
Fig. \ref{fig:SI3}. We included an estimated uncertainty $\Delta
  x_n=\Delta x$ in the
distances $x_n$ to the wall of the cell, and the corresponding (asymmetrical)
uncertainty in the computed current density. This
uncertainty arises from the uncontrolled deformation of the o-ring as
it is pressed against the wafer to seal in the electrolyte, so that
its distance $x'_n-x_n\approx 0.14\text{cm}\pm\Delta x$ to the wall of
the cell is not well determined. We estimate $\Delta x$
as the radius of the o-ring (Table \ref{t:xj}).
\begin{table}
  \centering
  \renewcommand{\arraystretch}{1.1}
    \begin{tabular}{rrr}
     $x'_n$(cm) &$x_n$(cm)&$j_\perp/I$ ($\text{cm}^{-2})$\\
     from edge& from wall&\\
     \hline
     0.2 &$ 0.06\pm0.05$ & $0.722^{+0.003}_{-0.007}$\\
     0.4 &$ 0.26\pm0.05$ & $0.672^{+0.018}_{-0.021}$\\
     0.6 &$ 0.46\pm0.05$ & $0.577^{+0.027}_{-0.028}$\\
     0.8 &$ 0.66\pm0.05$ & $0.464^{+0.028}_{-0.028}$\\
     1.0 &$ 0.86\pm0.05$ & $0.360^{+0.025}_{-0.023}$\\
     1.2 &$ 1.06\pm0.05$ & $0.275^{+0.019}_{-0.018}$\\
     1.4 &$ 1.26\pm0.05$ & $0.211^{+0.014}_{-0.013}$\\
     1.6 &$ 1.46\pm0.05$ & $0.167^{+0.010}_{-0.009}$\\
    \end{tabular}
  \caption{Normalized current density $j_\perp/I$ expected at different positions $x'_n$.}
  \label{t:xj}
\end{table}

In Fig. \ref{fig:sem} we show some SEM images of the sample $S_3$,
including top views and lateral views taken after
the optical characterization was completed and the sample was cut
along its center-line (see Sec. \ref{sec:R}) from
three regions around the left side, the center, and the right side
of the sample shown in Fig. \ref{fig:SI3}.
\begin{figure}
  \centering
  \includegraphics[width=.3\textwidth]{sema}
  \includegraphics[width=.3\textwidth]{semb}
  \includegraphics[width=.3\textwidth]{semc}
  \includegraphics[width=.3\textwidth]{semd}
  \includegraphics[width=.3\textwidth]{seme}
  \includegraphics[width=.3\textwidth]{semf}
  \caption{Top ((a), (b), and (c)) and lateral ((d), (e), and (f)) SEM
    micrographs of the sample $S_3$ taken from a region corresponding to the left
    side ((a) and (d)), center ((b) and (e)), and right side ((c) and
    (f)) along the center-line shown in Fig. \ref{fig:SI3}.}
  \label{fig:sem}
\end{figure}
We confirm that as we move away from the electrode, the pore
size and pore density diminish (panels (a) to (c) of
Fig. \ref{fig:sem}) and the sample becomes much thinner (panels (d) to
(f)). We remark that these micrographs were taken at three positions
that were not chosen to correspond to the eight locations at which we measured the
optical spectra. Thus, we didn't use SEM measurements for the quantitative
determination of neither the thickess nor the porosity; they were used
for the qualitative verification of the expected (Fig. \ref{fig:DE1})
and obtained (Table \ref{t:jpdv}) results. Actually, one of our
goals is to show that relatively inexpensive reflectance
measurements might be enough to characterize both the porosity and
etching rate variations along the sample.

@@

The results obtained from the reflectance fits are summarized in table
\ref{t:jpdv}.
\begin{table}
\centering
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{lrrrrr}
  Sample & position & density & porosity &
  thickness & rate\\
  ($I$ (mA)) &$x'_n$ (cm)&  $j$ ($\text{mA}/\text{cm}^2$) & $p$
       & $d$ ($\mu\text{m}$) & $v$ (nm/s)\\
\hline
$S_1$(5) &0.2 &$ 3.61^{+0.01}_{-0.03}   $&$0.56\pm0.03$ &$0.381\pm0.021$ &$  1.52\pm0.08$ \\
         &0.4 &$ 3.36^{+0.09}_{-0.11}   $&$0.59\pm0.02$ &$0.403\pm0.014$ &$  1.61\pm0.06$  \\
         &$0.6$  &$ 2.88^{+0.13}_{-0.14}$&$0.58\pm0.02$ &$0.342\pm0.015$ &$  1.37\pm0.06$ \\
         &$0.8$ &$ 2.32^{+0.14}_{-0.14} $&$0.57\pm0.02$ &$0.278\pm0.011$ &$  1.11\pm0.04$ \\
         &$1.0$ &$ 1.80^{+0.13}_{-0.12} $&$0.56\pm0.02$ &$0.224\pm0.009$ &$  0.90\pm0.03$ \\
         &$1.2$ &$ 1.37^{+0.10}_{-0.09} $&$0.56\pm0.02$ &$0.190\pm0.007$ &$  0.76\pm0.03$ \\
         &$1.4$ &$ 1.06^{+0.07}_{-0.06} $&$0.56\pm0.02$ &$0.153\pm0.005$ &$  0.61\pm0.02$ \\
         &$1.6$ &$ 0.83^{+0.05}_{-0.04} $&$0.56\pm0.02$ &$0.124\pm0.004$ &$  0.50\pm0.02$ \\
$S_2$(10) &$0.2$ &$ 7.22^{+0.03}_{-0.07}$&$0.64\pm0.04$ &$0.686\pm0.054$ &$  2.74\pm0.22$ \\
         &$0.4$ &$ 6.72^{+0.02}_{-0,21} $&$0.64\pm0.02$ &$0.694\pm0.025$ &$  2.78\pm0.10$ \\
         &$0.6$ &$ 5.77^{+0.27}_{-0.28} $&$0.64\pm0.03$ &$0.592\pm0.037$ &$  2.37\pm0.15$ \\
         &$0.8$ &$ 4.64^{+0.28}_{-0.28} $&$0.62\pm0.03$ &$0.530\pm0.034$ &$  2.12\pm0.14$ \\
         &$1.0$ &$ 3.60^{+0.25}_{-0.23} $&$0.61\pm0.03$ &$0.470\pm0.027$ &$  1.88\pm0.11$ \\
         &$1.2$ &$ 2.75^{+0.19}_{-0.18} $&$0.60\pm0.03$ &$0.414\pm0.026$ &$  1.66\pm0.10$ \\
         &$1.4$ &$ 2.11^{+0.14}_{-0.13} $&$0.59\pm0.03$ &$0.350\pm0.018$ &$  1.40\pm0.07$ \\
         &$1.6$ &$ 1.67^{+0.10}_{-0.09} $&$0.58\pm0.02$ &$0.302\pm0.014$ &$  1.21\pm0.05$ \\
$S_3$(20) &$0.2$ &$14.45^{+0.06}_{-0.14}$&$0.69\pm0.03$ &$1.208\pm0.047$ &$  4.83\pm0.19$ \\
         &$0.4$ &$ 13.44^{+0.35}_{-0.41}$&$0.72\pm0.02$ &$1.205\pm0.057$ &$  4.82\pm0.23$ \\
         &$0.6$ &$ 11.54^{+0.53}_{-0.55}$&$0.71\pm0.03$ &$1.050\pm0.058$ &$  4.20\pm0.23$ \\
         &$0.8$ &$  9.29^{+0.57}_{-0.55}$&$0.64\pm0.06$ &$0.766\pm0.088$ &$  3.06\pm0.35$ \\
         &$1.0$ &$  7.20^{+0.49}_{-0.47}$&$0.63\pm0.04$ &$0.540\pm0.037$ &$  2.16\pm0.15$  \\
         &$1.2$ &$  5.50^{+0.38}_{-0.36}$&$0.61\pm0.04$ &$0.449\pm0.035$ &$  1.80\pm0.14$ \\
         &$1.4$ &$  4.22^{+0.28}_{-0.26}$&$0.59\pm0.03$ &$0.369\pm0.018$ &$  1.48\pm0.07$ \\
         &$1.6$ &$  3.33^{+0.19}_{-0.17}$&$0.59\pm0.02$ &$0.338\pm0.014$ &$  1.35\pm0.06$ \\
\end{tabular}
\caption{\label{t:jpdv}
  Current density and fitted parameters for several positions on
  three samples:  porosity, thickness, and etching rate.}
\end{table}
The uncertainties in the fitted parameters $p$, $d$, and $v$ were
chosen as those that increase the sum of squared errors by 10\% with
respect to its minimum value.

From the data in Table \ref{t:jpdv} we can plot the fitted porosity vs.
the calculated density current $j_\perp$, as shown for our three
samples in Fig. \ref{fig:p}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pvsjerr}
  \caption{Porosity vs. current density for the three samples
    $S_1$, $S_2$, $S_3$. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$ (see text). We include a linear fit of the form
    $p=mj_\perp+b$ with parameters
    $m=(0.0122\pm0.001)\frac{\text{cm}^2}{\text{mA}}$ and
    $b=0.551\pm.005$.
    }
  \label{fig:p}
\end{figure}
Notice that for each sample the data points lie around straight lines,
except for one outlier point in each corresponding to position
$x'_1$. As discussed in Sec. \ref{sec:ps-grin-single}, those points
were very close to a wall of the electrolytic cell, so they were
affected by leakage currents towards the underside of the wall.
For this reason, we exclude those points from the following
analysis. We made a linear fit of the form $p=mj_\perp+b$ obtaining
\begin{equation}\label{eq:p}
  p\approx (0.0122\pm0.001)\frac{\text{cm}^2}{\text{mA}} j_\perp+(0.551\pm.005).
\end{equation}
Though the fit is reasonably good, it is noticeable that most of the data from
sample $S_2$ lie to the left of the fitted line while most of the data
from the other samples lie to the right. This discrepancies may be due
to the uncertainty in the positions $x_n$ (see Table \ref{t:xj}) due
to the ill defined distance from the edge of the sample (which roughly
corresponds to the position of the o-ring) to the edge of the cell. A
deformation of the o-ring when the cell is pressed against the wafer
would be equivalent to a rigid shift of the sample, i.e., to adding a
constant to all the positions $x_n$. Thus it is likely that the sign
and magnitude of that uncontrolled constant displacement changes among
samples.
